---
title: "xaringan tip:"
subtitle: "add a logo to all the slides"
author: "Garrick Aden-Buie"
institute: "<a href='https://www.garrickadenbuie.com/xaringan-tip-logo-all-slides'>garrickadenbuie.com/xaringan-tip-logo-all-slides</a>"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    lib_dir: libs
    includes:
      after_body: insert-logo.html
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: true
---

## Prepare your logo and slides

1. Download your logo. I've used the `xaringan` hex logo: [`xaringan.png`](https://github.com/rstudio/hex-stickers/blob/master/PNG/xaringan.png)

1. Download [`insert-logo.html`](https://github.com/gadenbuie/xaringan-logo/blob/master/insert-logo.html)

1. Add `insert-logo.html` to your `after_body` includes

  ```yaml
  output:
  xaringan::moon_reader:
    includes:
      after_body: insert-logo.html
  ```

1. Edit the `.logo` class in the CSS in `insert-logo.html` to use your logo,
   and adjust the `width`, `height` and position (`top`, `bottom`, `left`, and/or `right`) as needed<sup>*</sup>.
   
1. Use `class: hide-logo` to hide your logo on individual slides.
   
.footnote[
<sup>*</sup>Using the _Infinite Moon Reader_ can help here, but you have to save your slide file to trigger a full refresh when you edit `insert-logo.html`.
]

---


background-image: url(https://upload.wikimedia.org/wikipedia/commons/b/be/Sharingan_triple.svg)

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

???

Image credit: [Wikimedia Commons](https://commons.wikimedia.org/wiki/File:Sharingan_triple.svg)

---
class: center, middle

# xaringan

### /ʃaː.'riŋ.ɡan/

---
class: inverse, center, middle

# Get Started

---

# Hello World

Install the **xaringan** package from [Github](https://github.com/yihui/xaringan):

```{r eval=FALSE, tidy=FALSE}
devtools::install_github("yihui/xaringan")
```

--

You are recommended to use the [RStudio IDE](https://www.rstudio.com/products/rstudio/), but you do not have to.

- Create a new R Markdown document from the menu `File -> New File -> R Markdown -> From Template -> Ninja Presentation`;<sup>1</sup>

--

- Click the `Knit` button to compile it;

--

- or use the [RStudio Addin](https://rstudio.github.io/rstudioaddins/)<sup>2</sup> "Infinite Moon Reader" to live preview the slides (every time you update and save the Rmd document, the slides will be automatically reloaded in RStudio Viewer.

.footnote[
[1] 中文用户请看[这份教程](http://slides.yihui.name/xaringan/zh-CN.html)

[2] See [#2](https://github.com/yihui/xaringan/issues/2) if you do not see the template or addin in RStudio.
]

---
background-image: url(`r xaringan:::karl`)
background-position: 50% 50%
class: center, bottom, inverse

# You only live once!

---

# Hello Ninja

As a presentation ninja, you certainly should not be satisfied by the "Hello World" example. You need to understand more about two things:

1. The [remark.js](https://remarkjs.com) library;

1. The **xaringan** package;

Basically **xaringan** injected the chakra of R Markdown (minus Pandoc) into **remark.js**. The slides are rendered by remark.js in the web browser, and the Markdown source needed by remark.js is generated from R Markdown (**knitr**).

---

# remark.js

You can see an introduction of remark.js from [its homepage](https://remarkjs.com). You should read the [remark.js Wiki](https://github.com/gnab/remark/wiki) at least once to know how to

- create a new slide (Markdown syntax<sup>*</sup> and slide properties);

- format a slide (e.g. text alignment);

- configure the slideshow;

- and use the presentation (keyboard shortcuts).

It is important to be familiar with remark.js before you can understand the options in **xaringan**.

.footnote[[*] It is different with Pandoc's Markdown! It is limited but should be enough for presentation purposes. Come on... You do not need a slide for the Table of Contents! Well, the Markdown support in remark.js [may be improved](https://github.com/gnab/remark/issues/142) in the future.]

---
background-image: url(`r xaringan:::karl`)
background-size: cover
class: center, bottom, inverse

# I was so happy to have discovered remark.js!
